Restructuring Data for Exascale Scientific Productivity

### 2016-03-30 papers/2016-Supercomputing/paper.tex
intro start
introduction

\documentclass{sig-alt-gov2}
\pdfpagewidth=8.5in
\pdfpageheight=11in
%\usepackage{subfig}
\usepackage{subfigure}
\usepackage[pdftex]{}
\usepackage{graphicx}
%\usepackage{todonotes}
\usepackage{listings}
\lstset {% general command to set parameter(s)
         language=C,
     basicstyle=\footnotesize,               % print whole listing small
%     keywordstyle=\color{black}\bfseries, % underlined bold black keywords
%     identifierstyle =\color{black},  % nothing happens
%     commentstyle=\color{black}\emph, % white comments
     %stringstyle=\ttfamily,          % typewriter type for strings
%     stringstyle=\color{black},       % typewriter type for strings
         tabsize=4,
         showtabs=false,
     showstringspaces=false}
%can't figure this one out for particles bandwidth
%\usepackage[caption,label]{subfig}

%\newcommand{\TITLE}{D\textsuperscript{\huge{2}}T: Doubly Distributed Transactions for High Performance and Distributed Computing}

@@

% in order for balance columns to work, it has to be before begin document...
%\balancecolumns

@@

%\conferenceinfo{PDSW'15,} {November 17, 2015, Austin, Texas}
%\CopyrightYear{2015}
%\crdata{978-1-4503-1103-8/11/11}
%\clubpenalty=10000
%\widowpenalty = 10000

@@

@@

%\category{D.4}{Software}{Operating Systems}
%\category{D.4.7}{Operating Systems}{Organization and Design}[hierarchical design]

%\terms{Design, Performance}

@@

%\begin{figure}[htbp]
%\vspace{-0.10in}
%\centering
%\includegraphics[width=\columnwidth]{images/arch-mapping}
%\vspace{-0.20in}
%\caption{Architecture and Component Mapping}
%\label{fig:arch-mapping}
%\vspace{-0.15in}
%\end{figure}

@@

validation/experiments (XGC1 only for now, 1 & 2 buckets, all other factors):\\
\begin{enumerate}
\item Performance writing (A orig, B 2 buckets)
\item Performance reading (A orig, B 2 buckets, C bucket 1, D, bucket 2)
\item Visualization diff (3-d)
\item numeric evaluation diff (to get past criticism of 3-d hiding errors)
\item derived quantity
\item interpolation validation
\end{enumerate}

>>>>

\documentclass{sig-alt-gov2}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% \usepackage{subfig}
\usepackage{subfigure}
\usepackage[pdftex]{}
\usepackage{graphicx}
% \usepackage{todonotes}
\usepackage{listings}
\usepackage{comment}
\lstset {% general command to set parameter(s)
  language=C,
  basicstyle=\footnotesize,               % print whole listing small
  % keywordstyle=\color{black}\bfseries, % underlined bold black keywords
  % identifierstyle =\color{black},  % nothing happens
  % commentstyle=\color{black}\emph, % white comments
  % stringstyle=\ttfamily,          % typewriter type for strings
  % stringstyle=\color{black},       % typewriter type for strings
  tabsize=4,
  showtabs=false,
  showstringspaces=false}
% can't figure this one out for particles bandwidth
% \usepackage[caption,label]{subfig}

% \newcommand{\TITLE}{D\textsuperscript{\huge{2}}T: Doubly Distributed Transactions for High Performance and Distributed Computing}

@@

% in order for balance columns to work, it has to be before begin document...
% \balancecolumns

@@

% \conferenceinfo{PDSW'15,} {November 17, 2015, Austin, Texas}
% \CopyrightYear{2015}
% \crdata{978-1-4503-1103-8/11/11}
% \clubpenalty=10000
% \widowpenalty = 10000

@@

% \category{D.4}{Software}{Operating Systems}
% \category{D.4.7}{Operating Systems}{Organization and Design}[hierarchical design]

% \terms{Design, Performance}

@@

@@

This paper describes our initial foray into hierarchical partitioning techniques
to match the structure of storage in future systems. We have developed three
sets of techinques for partitioning scientific data from large scale
applications, evaluated these techniques on our local cluster to gain deeper
understanding of the cost-benefit tradeoffs with respect to computational time,
storage time, storage space, access speeds and power consumption, and utilized
microbenchmarks to extrapolate our results to future use cases. Our research is
driven by a combination of application user requirements and data consumption
use cases, such as scientific visualization. To aid in adoption and
experimentation, we have integrated our techniques with the ADIOS high
performance I/O middleware library and the Visit visualization application.

The three broad techniques we study in this paper are bit-based splitting of
double precision floating point data, spatial dimensional sampling of data, and
a temporal interpolation based data prediction technique. In
Section~\ref{details} we provide details on each of these techniques and discuss
the various tradeoffs each technique emobdies. Our evaluation platform presents
a two level storage hierarchy with local SSDs and a remote lustre parallel file
system. Both storage targets have different performance characteristics, and
more details on the evaluation platform are presented in Section~\ref{hardware}.
With this background we present our results in Section~\ref{performance} and
discussion in Section~\ref{res-discussion}. This work is the first step in a
comprehensive new direction for data management at large scale and we discuss
the future of this effort and conclusions in Section~\ref{future}.

% \begin{figure}[htbp]
%   \vspace{-0.10in}
%   \centering
%   \includegraphics[width=\columnwidth]{images/arch-mapping}
%   \vspace{-0.20in}
%   \caption{Architecture and Component Mapping}
%   \label{fig:arch-mapping}
%   \vspace{-0.15in}
% \end{figure}

@@

validation/experiments (XGC1 only for now, 1 \&1 2 buckets, all other factors):\\
\begin{enumerate}
\item Performance writing (A orig, B 2 buckets)
\item Performance reading (A orig, B 2 buckets, C bucket 1, D, bucket 2)
\item Visualization diff (3-d)
\item numeric evaluation diff (to get past criticism of 3-d hiding errors)
\item derived quantity
\item interpolation validation
\end{enumerate}
